First results of developing a Swedish parser based on a wide-coverage grammar\\ eller Combining resources into a Swedish parser eller Bootstrapping a Swedish parser \\ eller A grammar-based Swedish parser from already existing resources

### 2011-10-13 doc/paper/Paper.tex
paper, evaluation, mapping, plannig.

\title{First results of developing a Swedish parser based on a wide-coverage grammar}
\author{Malin Ahlberg \& Ramona Enache
%\and
%Co Author \qquad\qquad 
\institute{Department of Computer Science \& Engineering, Gothenburg University, Sweden}
}
\def\titlerunning{First results of developing a grammar based Swedish parser}
\def\authorrunning{M. Ahlberg}
\begin{document}
\maketitle

\begin{abstract}
This paper describes on going work of a rule-based, open-source
parser for Swedish. The central component will be a wide-coverage grammar
implemented in the formalism Grammatical Framework (GF). The
resulting parser will be the first deep Swedish grammar-based parser  and
will give a full syntactic analysis of the input sentences.
In addition to GF, we use two other main resources: the Swedish
treebank Talbanken and the electronic lexicon SALDO.
% ha med detta?
The grammar will be highly reusable, chosen 
parts of the it can be used in applications dealing with
%controlled or free
natural language. GF also provides libraries for compiling
grammars to a number of programming languages.
% allow easy interaction with other programs and grammars
%>> something very commercial, interesting and outstanding here please!

@@

@@

%compare!!
\section{Related work}
Language technology for Swedish is an area of much interesting research.
There are tools for lexical extractions, such as
Extract for supervised lexicon extraction and
FM\cite{MarkusForsberg2007} for programming lexical resources.
Among other parsers for Swedish, the statistical MaltParser\cite{malt}
which was trained on Talbanken, is worth mentioning. 
CassSwe (Kokkinakis and Johansson-Kokkinakis, 1999) is based on finite state cascades,
whereas the shallow parser GTA (Knutsson, Bigert and Kann, 2003) relies on rules of 
a context free grammar. Both GTA and CassSwe operate on POS tagged text.

>>>>

\title{First results of developing a Swedish parser based on a wide-coverage grammar\\
        eller Combining resources into a Swedish parser
        eller Bootstrapping a Swedish parser \\
        eller A grammar-based Swedish parser from already existing resources}
\author{Malin Ahlberg \& Ramona Enache
%\and
%Co Author \qquad\qquad 
\institute{Department of Computer Science \& Engineering, Gothenburg University, Sweden}
}
\def\titlerunning{First results of developing a grammar based Swedish parser}
\def\authorrunning{M. Ahlberg}
\begin{document}
\maketitle

\begin{abstract}
This paper describes on going work of a rule-based, open-source
parser for Swedish. The central component will be a wide-coverage grammar
implemented in the formalism Grammatical Framework (GF), from which we 
derive?? a deep parser.
In addition to GF, we use two other main resources: the Swedish
treebank Talbanken and the electronic lexicon SALDO.
The resulting parser will 
will give a full syntactic analysis of the input sentences.
Since all the parser will be freely available, 
% ha med detta?
it will be highly reusable and chosen parts of the the grammar can be used in
applications dealing with
%controlled or free
natural language. GF also provides libraries for compiling
grammars to a number of programming languages.
% allow easy interaction with other programs and grammars
%>> something very commercial, interesting and outstanding here please!

@@

%compare!!
\section{Related work}
Language technology for Swedish is an area of much interesting research.
There are tools for lexical extractions, such as
Extract for supervised lexicon extraction and
FM\cite{MarkusForsberg2007} for programming lexical resources.
There are two other deep grammar-based parser for Swedis,
SICS (Manny Raynen, ) and ? (Mats Wirén,?). Unlike our parser, 
they are not freely commercialized.
Among other parsers for Swedish, the statistical MaltParser\cite{malt}
which was trained on Talbanken, is worth mentioning. 
CassSwe (Kokkinakis and Johansson-Kokkinakis, 1999) is based on finite state cascades,
whereas the shallow parser GTA (Knutsson, Bigert and Kann, 2003) relies on rules of 
a context free grammar. Both GTA and CassSwe operate on POS tagged text.

@@
